A Gentle Introduction into Structural Causal Models

### 2021-05-14 draft.Rmd
reference color adjustment

---
title: "A Gentle Introduction into Structural Causal Models"
author: 
- Daniel Saggau $\boldsymbol{\cdot}$ `daniel.saggau@campus.lmu.de`
- Department of Statistics, Ludwig Maximilian University Munich, Germany
date: " April 5th, 2021"
output: 
  pdf_document:
        number_sections: yes
        fig_caption: yes
fontsize: 12
linestretch: 1.5
citation_package: --biblatex
bibliography: [ref.bib]
nocite: '@*'

@@

\newpage
\tableofcontents
\newpage

>>>>

---
title: "A Gentle Introduction into Structural Causal Models"
author: 
- Daniel Saggau $\boldsymbol{\cdot}$ `daniel.saggau@campus.lmu.de`
- Department of Statistics, Ludwig Maximilian University Munich, Germany
date: " April 5th, 2021"
output: 
  pdf_document:
        number_sections: yes
        fig_caption: yes
link-citations: yes
linkcolor: blue
fontsize: 12
linestretch: 1.5
citation_package: --biblatex
bibliography: [ref.bib]
nocite: '@*'

@@

\newpage
\hypersetup{linkcolor=black}
\tableofcontents
\newpage

\hypersetup{linkcolor=blue}
